{RandomRationalPoints} package for \emph{Macaulay2}

### 2021-01-20 FastLinAlg/Paper/RandomRationalPoints.tex
updated addresses

\begin{document}
\title{{RandomRationalPoints} package for \emph{Macaulay2}}
\author{Sankhaneel Bisui}
\email{sbisui@tulane.edu}
\address{Tulane University}
\author{Zhan Jiang}
\email{zoeng@umich.edu}
\address{University of Michigan}
\author{Sarasij Maitra}
\email{sm3vg@virginia.edu}
\address{University of Virginia}
\author{Thai Nguyen}
\email{tnguyen11@tulane.edu}
\address{Tulane University}
\author{Karl Schwede}
\email{schwede@math.utah.edu}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
\date{\today}

@@

    There is an existing package called {\tt RandomPoints}, which we took inspiration from, which aims to find \emph{all} the rational points of a variety; our aim here is to find one point quickly, even if it is not rational.  
    We provide some functions that apply different strategies to generate random rational points for the given variety. We also provide functions that will expedite the process of determining properties of the singular locus of $X$.% when combined with the functions provided in the package {\tt FastLinAlg}.

@@

\begin{example}Now we work over a larger field.
        {{\small\color{blue}
        ~~
        \begin{quote}
\begin{verbatim}
i6 : S = ZZ/211[x_1..x_10];

@@

    \begin{example}
        Finally, we allow our functions to extend our field.
        {{\small\color{blue}
        ~~
        \begin{quote}
        \begin{verbatim}
i12 : time randomPoints(J, Strategy => LinearIntersection, ExtendField => true)
-- used 0.0612306 seconds

@@

This method works by calling {\tt randomCoordinateChange} (see \Cref{helper}) before dropping some variables.  It passes the options {\tt Replacement}, {\tt MaxCoordinatesToReplace}, {\tt Homogeneous} to that function.
%The user can also specify the same options as before to be passed on to the {\tt randomCoordinateChange} function.

>>>>

\begin{document}
\title{{RandomRationalPoints} package for \emph{Macaulay2}}
\author{Sankhaneel Bisui}
\email{sbisui@tulane.edu}
\address{Department of Mathematics, Tulane University, New Orleans, LA 70118}
\author{Zhan Jiang}
\email{zoeng@umich.edu}
\address{Department of Mathematics, University of Michigan, Ann Arbor, MI 48109}
\author{Sarasij Maitra}
\email{sm3vg@virginia.edu}
\address{Department of Mathematics, University of Virginia, Charlottesville, VA 22904}
\author{Thai Nguyen}
\email{tnguyen11@tulane.edu}
\address{Department of Mathematics, Tulane University, New Orleans, LA 70118}
\author{Karl Schwede}
\email{schwede@math.utah.edu}
\address{Department of Mathematics, University of Utah, 155 S 1400 E Room 233, Salt Lake City, UT, 84112}
%\date{\today}

\thanks{Schwede was supported by NSF Grant \#1801849, NSF FRG Grant \#1952522 and a Fellowship from the Simons Foundation.}

@@

    There is an existing package called {\tt RandomPoints}, which we took inspiration from, which aims to find \emph{all} the rational points of a variety; our aim here is to find one point quickly, even if it is not rational.  
    We develop functions that apply different strategies to generate random rational and geometric points onn the given variety. We also provide functions that will expedite the process of determining properties of the singular locus of $X$.% when combined with the functions provided in the package {\tt FastLinAlg}.

@@

\begin{example}
    Now we work over a larger field.
    {{\small\color{blue}
    \begin{quote}
\begin{verbatim}
i6 : S = ZZ/211[x_1..x_10];

@@

    \begin{example}
        Finally, we allow our functions to extend our field.
        {{\small\color{blue}
        \begin{quote}
        \begin{verbatim}
i12 : time randomPoints(J, Strategy => LinearIntersection, ExtendField => true)
-- used 0.0612306 seconds

@@

This method works by calling {\tt randomCoordinateChange} (see \Cref{helper}) before dropping some variables.  It passes the options {\tt Replacement}, {\tt MaxCoordinatesToReplace}, {\tt Homogeneous} to that function.
%The user can also specify the same options as before to be passed on to the {\tt randomCoordinateChange} function.
\begin{comment}~~
